Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-04-29 overleaf/biometric_vectorization_example.tex
Did a pass on Section 5.

\subsection{Example: Biometric}

We start from MPC Source:

@@

\subsubsection{Phase 1 of Basic Vectorization}

@@

\subsubsection{Phase 2 of Basic Vectorization}

@@

\subsubsection{Phase 3 of Basic Vectorization}

@@

// i is redundant for min_sum!2, min_sum!4 but not for !12![i]!
for i in range(0, N!0):
  min_sum!2 = PHI(min_sum!1, min_sum!4) 
  !1!2[i] = (sum!3[i] < min_sum!2)
  min_sum!4 = MUX(!1!2[i], sum!3[i], min_sum!2)

@@

\subsubsection{Phase 4 of Basic Vectorization}

And this phase adds SIMD operations:

>>>>

\subsubsection{Example: Biometric}

We now demonstrate the workings of the basic algorithm on our running example. Recall the MPC Source for Biometric:

@@

\paragraph{Phase 1 of Vectorization Algorithm}

@@

\paragraph{Phase 2 of Vectorization Algorithm}

@@

\paragraph{Phase 3 of Vectorization Algorithm}

@@

// i is redundant for min_sum!2, min_sum!4 but not for !12![i]
for i in range(0, N!0):
  min_sum!2 = PHI(min_sum!1, min_sum!4) 
  !1!2[i] = (sum!3[i] < min_sum!2)
  min_sum!4 = MUX(!1!2[i], sum!3[i], min_sum!2)

@@

\paragraph{Phase 4 of Basic Vectorization}

This phase adds SIMD operations:
